Working document to try to explain why/how ATAs influence coexistence in an intuitive way for referee 3

### 2023-07-28 paper/ExplanationOfATAEffectsWorkingDoc.tex
finished a complete draft of the new explanatory material, about to start putting it into the paper

>>>>

Fig. \ref{fig:lognormal_fecundidities_explanatory} is similar to 
Fig. \ref{fig:beta_fecundidities_explanatory}, but is based on the log-normal 
fecundities lottery model instead of the beta fecundities lottery model. 
The figure illustrates that the potential for storage events is equivalent in
the upper and lower tails of the $EC$ distribution (labelled ``right'' and ``left'',
respectively, on panels A-C). That is why ATA effects are fairly modest for the 
log-normal fecundities lottery model for the both the left- and right-tail
associated cases.
